State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to figures

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.

\begin{figure}
	\begin{center}
		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
	\end{center}
	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:ExampleFieldAndSensorsDataAndPSD} 
\end{figure}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.

>>>>

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
\begin{figure*}
	\begin{center}
		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
	\end{center}
	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
\end{figure*}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.
